Weather Data Integration and Assimilation System\\

### 2020-02-14 method/sec_3-microservice.tex
Change all to \cref

When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in Section \ref{se:architectural_decisions}. But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
Applications built from microservices aim to be as decoupled and as cohesive as possible. They own their own domain logic and act more as filters in the classical Unix sense. After receiving a request, applying logic as appropriate and producing a response. And it uses simple RESTish protocols rather than complex protocols.
\dbc{RESTish or RESTful?}

@@

Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the Section \ref{se:discussion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture \hl{for server requests on demand}}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of Figure \ref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section Section \ref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in Section \ref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handling requests asynchronously.}
    \label{fi:wdias_micro_async}
\end{figure}
Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
Each adapter follows the concept of database per service as mentioned in the section Section \ref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.

As shown in Figure \ref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back. However, as shown in Figure \ref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not. Here is uses the microservice pattern of Section \ref{subse:sagas} while processing the Grid data. First it store the data and respond back to the user. Then publish an event, and another service listen to those events and process the data and update the system status.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation of \acrshort{wdias} microservices.}
    \label{fi:wdias_micro_separation}
\end{figure}
The figure \ref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}. As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
Apart from that, as we further discuss in Section \ref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.

@@

\emph{Extensions} endpoints for configure extensions. These details describes in the Section \ref{se:data_preprocess}.

>>>>

When building communication endpoints, \hl{many architecture approach with putting significant smart into the communication mechanism.} One good example is \acrshort{esb} what we discussed in \cref{se:architectural_decisions}. But microservice follows alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
Applications built from microservices aim to be as decoupled and as cohesive as possible. They own their own domain logic and act more as filters in the classical Unix sense. After receiving a request, applying logic as appropriate and producing a response. And it uses simple RESTish protocols rather than complex protocols.
\dbc{RESTish or RESTful?}

@@

Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalability of the system further. This will be more discuss in the \cref{se:discussion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\acrshort{wdias} Microservices}
\label{sebse:wdias_microservices}
As seen in Figure of \cref{fi:wdias_micro_on_demand} and \cref{fi:wdias_micro_async} each circle represents a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture \hl{for server requests on demand}}
    \label{fi:wdias_micro_on_demand}
\end{figure}
Left side of \cref{fi:wdias_micro_on_demand} shows the import modules of the \acrshort{wdias}, and right side shows the export modules. As it explained section \cref{subse:dumb_pipes}, each import microservice only do specific task of converting and forwarding the request to the correct data adapter module.
For each data type, there is a adapter microservice is running which is optimized to storing such type of data. And the metadata data of the timeseries store using \acrshort{rdbms} which gives more performance over retrieving metadata data. The metadata is cached with In-Memory database to fast access as mentioned in \cref{subse:redis}.
The system generate a unique identifier for each timeseries, and throw out the \acrshort{wdias}, other microservice use it to handle data for fast access.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_async-v3.jpg}
    \caption{\acrshort{wdias} architecture for handling requests asynchronously.}
    \label{fi:wdias_micro_async}
\end{figure}
Export module microservice follows the same concepts and provide the capability to export the data into required formats of the weather models.
Each adapter follows the concept of database per service as mentioned in the section \cref{subse:database_per_service}. This gives the freedom for \acrshort{wdias} to scale better with \acrshort{k8s}.

As shown in \cref{fi:wdias_micro_on_demand}, when a smaller size request come to the system, it handle on demand and response back. However, as shown in \cref{fi:wdias_micro_async}, when a request with larger size come to the system, it store the data for asynchronously process the data and response with a unique id which can use to verify whether data processed successfully or not. Here is uses the microservice pattern of \cref{subse:sagas} while processing the Grid data. First it store the data and respond back to the user. Then publish an event, and another service listen to those events and process the data and update the system status.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/separation_microservices-v3.jpg}
    \caption{Separation of \acrshort{wdias} microservices.}
    \label{fi:wdias_micro_separation}
\end{figure}
The \cref{fi:wdias_micro_on_demand} show the clear separation of microservices into the modules of the \acrshort{wdias}. As it shown, each adapter has isolated database, and database is hosted separately for the high performance.
Apart from that, as we further discuss in \cref{se:data_preprocess}, the extension modules are running separately such as Interpolation, Transformation and Validation etc.
The Extension Adapter allow users to register new triggers for the extensions. And extension scheduler triggers the events based on time and extension handler triggers event based on data change.

@@

\emph{Extensions} endpoints for configure extensions. These details describes in the \cref{se:data_preprocess}.

### 2020-02-14 method/sec_4-db_struct.tex
Change all to \cref

WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in Section \ref{subse:database_per_service}.
Following chapters described the usage of databases in WDIAS and reason behind the selection.

@@

%There are lots of \acrshort{rdbms} available and for 
\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
%SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \ref{se:data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
\ref{subse:redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.
\dbc{First start with a brief discussion on why a RDBMS is needed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{has higher number of usage and support. Database is written in Golang programming language, and} has higher performance, and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.

Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \emph{Database per Service} as mentioned in Section \ref{subse:database_per_service}.
But further, it split into two services, referring to the Section \ref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among few servers based on valueType key attribute of timeseries.
Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.

@@

\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented databse, as it has the Geo searching capabilities.
\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports:
\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of EDIAS above.}
\begin{itemize}
  \item Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}
\acrshort{mongodb} geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}. Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
In Section \ref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \ref{se:data_preprocess}

>>>>

WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in \cref{subse:database_per_service}.
Following chapters described the usage of databases in WDIAS and reason behind the selection.

@@

%There are lots of \acrshort{rdbms} available and for 
\acrshort{wdias} is using SQL as the \acrfull{rdbms}. 
%SQL database has fewer version of open source and it is also possible to gain better performance with commercial versions. 
Since WDIAS scope is to using open source tools, it is using \acrshort{mysql} as persistent database for storing timeseries metadata described above.
One instance of \acrshort{mysql} is using only by adapter-metadata service.
Other than that, another instance of \acrshort{mysql} is using for adapter-extension which will be describe in more detail \cref{se:data_preprocess}.
\acrshort{mysql} is used only for these services, those will only keep the consistency of the schema for timeseries metadata and extension metadata.
As mentioned in \cref{subse:redis}, it uses \acrshort{redis} instance is using for caching the data from \acrshort{mysql}, since the \acrshort{mysql} database instances, itself not going to get much load.
Other than MySQL, there are many open source databases can be used to replace the same functionality.
\dbc{First start with a brief discussion on why a RDBMS is needed}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Timeseries Database}
\label{subse:influxdb}
Among several timeseries open source databases, \acrshort{influxdb} \cite{influxdbInfluxDBDocumentation} \hl{has higher number of usage and support. Database is written in Golang programming language, and} has higher performance, and has following supports;
\begin{itemize}
  \item Open timeseries DB with MIT license
  \item Support SQL-Like query language
  \item Clustering available with a commercial version
\end{itemize}
Other than \acrshort{influxdb}, another database is Elastic Search which is mainly using for indexing for searching.
With changing the configurations of the \acrshort{influxdb}, it is possible to adapt as required. As mention in \cite{influxdbInfluxDBDocumentation}, 
\acrshort{influxdb} can setup on a computer which will give the required performance. Going further, users can use commercial version of \acrshort{influxdb} in order to gain more performance.

Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \emph{Database per Service} as mentioned in \cref{subse:database_per_service}.
But further, it split into two services, referring to the \cref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among few servers based on valueType key attribute of timeseries.
Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.

@@

\acrshort{wdias} is using \acrshort{mongodb} as the document-oriented databse, as it has the Geo searching capabilities.
\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports:
\dbc{Need for a mix of relational, time series, document stores, and in-memory need to be first mentioned and justified in high-level design of EDIAS above.}
\begin{itemize}
  \item Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}
\acrshort{mongodb} geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}. Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
In \cref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{In-Memory Database}
\label{subse:redis}
\acrshort{wdias} is using \acrshort{redis} \cite{redisRedisDocumentation} as the In-Memory database, since it's widely using tool with good support, and it support few other features such as Publisher Subscriber capabilities.
\acrshort{redis} is an open source (BSD licensed), used as a database, cache. Clustering is available for scalability.
\acrshort{redis} uses as in-memory caching for fast access of repreative access data in adapter-metadata and adapter-extension.
Other than that, adapter-status uses \acrshort{redis} as key value pair store for getting the status for async handling requests such as storing Grid data.
In adapter-extension uses Redis's Publisher Subscriber capabilities in order to create a cron job in extension-scheduler when new extension create on \cref{se:data_preprocess}

### 2020-02-14 results/sec_0-introduction.tex
Change all to \cref

This chapter includes performance study of the \acrshort{wdias}. In Section \ref{se:test_plan} describes the planned method of testing the system.
In the next Section \ref{se:workload} describes the logic behind creating the workload to do the performance testing planned in Section \ref{se:test_plan}.
Following Section \ref{se:observations} includes the results observed while performance study. And summarised the observations in the next Section \ref{se:discussion}.

>>>>

This chapter includes performance study of the \acrshort{wdias}. In \cref{se:test_plan} describes the planned method of testing the system.
In the next \cref{se:workload} describes the logic behind creating the workload to do the performance testing planned in \cref{se:test_plan}.
Following \cref{se:observations} includes the results observed while performance study. And summarised the observations in the next \cref{se:discussion}.

### 2020-02-14 results/sec_2-workload.tex
Fix with Figure
Change all to \cref

For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed. Since grid locations have different metadata structure as described in Section \ref{se:db_struct}, those data handle separately. But the locationId of grid and scalar data types have the same effect when define a timeseries.

In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. jmeter best practices lean\_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in Section \ref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This occurs in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

@@

The test plans mentioned in Section \ref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:

@@

In the \ref{fi:test_prod_throughtput_shaping_timer} shows the Throughput Shaping Timer configurations for the All test case.

@@

It allows to run particular test plan which are described in Section \ref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{System Configuration}}
\label{subse:test_sys_config}
As described in the Section \ref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud.

A detailed description of setting up the \acrshort{eks} available as \cite{KarunarathneWdias/Amazon_EKS.md:EKS} within the main repository of the \acrshort{wdias}.
\acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system. During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in Table \ref{tab:aws_eks_nodes}.

@@

Users can use one of above features to fine-tune the \acrshort{wdias} to perform better. For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes. Pods are assigned to the nodes \ref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core} -- metadata, extensions, query, status and extension services
    \item \emph{grid} -- grid adapter, import and export grid data
    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
    \item \emph{test} -- jMeter and metric server
\end{itemize}
Figure \ref{fi:eks_node_setup} show the overview of show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
The databases uses for data consistency and performance in storage optimization with search capabilities. But because of that, it only possible to run one instance of those. In the \acrshort{wdias}, the MySQL and MongoDb are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for grid data type. In order to keep up with the pace, those microservice pods are assign to dedicated nodes in order to increase the performance of inter-service communication.

>>>>

For grid data, it uses static 100 grid locations which based on how is \acrshort{api} exposed. Since grid locations have different metadata structure as described in \cref{se:db_struct}, those data handle separately. But the locationId of grid and scalar data types have the same effect when define a timeseries.

In the \acrshort{jmeter} Best Practices, \say{If your test needs large amounts of data - particularly if it needs to be \emph{randomised} create the test data in a file that can be read with CSV Data set. This avoids wasting resources at run-time. jmeter best practices lean\_mean}. Rather providing the randomness in run time, the timeseries stored with the random order which satisfy the percentage of 70\% Scalar, 20\% Vector and 10\% Grid as mentioned in \cref{se:test_plan}.
Before running the test cases, it generate the metadata for timeseries and write into a CSV file which is shared among the threads in the \acrshort{jmeter}. This occurs in the setup phase of the test cases. The metadata CSV file arrange in a way that within each 10 lines, 7 lines are Scalar timeseries, 2 lines are Vector timeseries, and 1 line is a Grid timeseries.

@@

The test plans mentioned in \cref{se:test_plan} are implemented via the \acrshort{jmeter}. The following list shows the all the test cases used for the performance testing:

@@

In the \cref{fi:test_prod_throughtput_shaping_timer} shows the Throughput Shaping Timer configurations for the All test case.

@@

It allows to run particular test plan which are described in \cref{se:test_plan}. Also possible to run the all the test plans in order with given \emph{REQ\_SIZE} or for all the \emph{REQ\_SIZE}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{System Configuration}}
\label{subse:test_sys_config}
As described in the \cref{se:microservice}, the \acrshort{wdias} is mainly focus on microservice architecture and implemented on top of kubernetes. \acrfull{k8s} is an open-source system for automating deployment, scaling, and management of containerized applications. For the performance study uses \acrfull{eks}. There are many \acrshort{k8s} solutions available such as GCP, Azure, and Digital Ocean on the cloud.

A detailed description of setting up the \acrshort{eks} available as \cite{KarunarathneWdias/Amazon_EKS.md:EKS} within the main repository of the \acrshort{wdias}.
\acrshort{k8s} is a planet scaling tool \cite{LinuxFoundationProduction-GradeKubernetes}, and users can tweak the configuration to run the \acrshort{wdias} as per the required level of load on the system. During the performance test of the \acrshort{wdias}, it uses maximum of 300 \acrshort{rps} with providing to the system with increasing load, and monitor the auto scalability of the system with measuring other performance parameters mentioned in \cref{tab:aws_eks_nodes}.

@@

Users can use one of above features to fine-tune the \acrshort{wdias} to perform better. For the moment, \acrshort{wdias} helm charts uses node Affinity in order to use the same charts within local setup with one node and work the same charts on a \acrshort{k8s} cluster with multiple nodes. Pods are assigned to the nodes \cref{tab:aws_eks_nodes} based on the node label as below;
\begin{itemize}
    \item \emph{core} -- metadata, extensions, query, status and extension services
    \item \emph{grid} -- grid adapter, import and export grid data
    \item \emph{scalar} -- scalar and vector adapters, import and export of same data types
    \item \emph{test} -- jMeter and metric server
\end{itemize}
\cref{fi:eks_node_setup} show the overview of show the nodes are setup and each microservices are assigned to each node, the connectivity of the nodes, and the data interactions via the arrows.
The databases uses for data consistency and performance in storage optimization with search capabilities. But because of that, it only possible to run one instance of those. In the \acrshort{wdias}, the MySQL and MongoDb are not getting higher load as adapter databases such as InfluxDB for scalar and vector data types, and netCDF for grid data type. In order to keep up with the pace, those microservice pods are assign to dedicated nodes in order to increase the performance of inter-service communication.
